Solar jet observed at the limb in SDO/SST

### 2016-05-19 paper/ms_temp_paper.tex

>>>>

The authors use a Differential Emission Measure (DEM) to obtain a temperature response from the SDO/AIA measurements.
The temperature response is a combination of the wavelength response from the instrument and the contribution function which describes the emission from a given temperature.
When using such a scheme, we need to decide on a general DEM profile to be applied to all pixels.
Utilising a narrow Gaussian seems to provide the most accurate values when compared to synthetic observations.
